Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-16 paper_comparison/paper_comparison/paper_comparison.Rmd
finish prototype of the power plot

>>>>

```{r cache = TRUE}
target_sigma <- c(4.51, 3.52, 2.74, 2.14, 1.66, 1.29, 1.01, 0.79, 0.61, 0.48, 0.37)

es <- map_dbl(target_sigma, ~log(poly_model(shape = 2, x = rand_uniform(), sigma = .x)$effect_size(n = 100)))
```

```{r}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1)) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power")

ex_dat <- poly_model(shape = 2, x = rand_uniform(), sigma = 1)$gen(n = 100)
plist <- list()
j <- 0

for (i in target_sigma) {
  j <- j + 1
  plist[[j]] <- 
  VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform())$
                  gen(n = 100, computed = select(mutate(ex_dat, e = sqrt(i) * e), x, e)), theme = theme_light(), 
              remove_axis = TRUE, 
              remove_grid_line = TRUE) +
    ggtitle(round(es[j], 1))
}

patchwork::wrap_plots(plist)
```

### 2022-11-16 paper_comparison/paper_comparison/paper_comparison.tex
finish prototype of the power plot

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-8-1}

@@

\caption{...}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1} \end{center}

>>>>

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-2} \end{center}

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1}

@@

\caption{...}\label{fig:unnamed-chunk-9}
\end{figure}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-10-1} \end{center}
